Goals and Tasks

### 2020-05-12 README.Rmd
Update to readme

>>>>

## Location Scale Regression Model

## Working with Location Scale Regression Boost Model
First, you need to install the `asp20model` &  `asp20boost` package from GitLab and load it:

```{r installation, eval = 3}
install.packages("devtools")
devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")
library(asp20boost)
```

```{r}
model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
gradient_boost(model, 
              stepsize = 0.001, maxit = 1000,
              abstol = 0.001,
              verbose = FALSE)
plot(x, y)
lines(x,model$fitted_location)
#Todo do create similar graphic
curve(x + 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)
curve(x - 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)

```
